% This file was converted to LaTeX by Writer2LaTeX ver. 1.1.7
% see http://writer2latex.sourceforge.net for more info
\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=Daniel Church Resume, pdfauthor=Daniel Church, pdfsubject=, pdfkeywords=}
% Text styles
\newcommand\textstyleStrongEmphasis[1]{\textbf{#1}}
\newcommand\textstyleBulletSymbols[1]{\textrm{#1}}
% Outline numbering
\setcounter{secnumdepth}{0}
\makeatletter
\newcommand\arraybslash{\let\\\@arraycr}
\makeatother
% List styles
\newcommand\liststyleLi{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
% Page layout (geometry)
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{9.4251995in}
\setlength\textwidth{6.9251995in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\setlength\tabcolsep{1mm}
\renewcommand\arraystretch{1.3}
\title{Daniel Church Resume}
\author{Daniel Church}
\date{2011-07-25}
\begin{document}
{\centering\sffamily
3208 Lyndale Ave. S \#8, Minneapolis MN 55408\newline
Email: dchurch000@gmail.com Tel: +1-651-206-7515
\par}

\section[Daniel Church]{Daniel Church}
\subsection[Profile]{Profile}
Accomplished software developer with 10+ years of experience in the field including designing and implementing SQL databases, software testing and patching, web security assessments and UNIX system administration.

{\bfseries
Areas of expertise include:}

{\bfseries
Software Development (Perl, Shell, SQL, PHP, JavaScript, HTML, CSS, XML, XSLT, Java, AJAX)}

{\bfseries
UNIX System Administration and Security}

{\bfseries
SQL Database Design and Implementation}

{\bfseries
Graphic Design}

\subsection[Education]{Education}
\ \ Sep, 2003 --- Dec, 2007\ \ UW River Falls

Undergraduate\newline
Computer Science \& Information Systems

\ \ Jan, 2010 --- Present\ \ Dunwoody Technical

Undergraduate\newline
CWEB

\subsection[Work Experience]{Work Experience}
\ \ Aug, 2009 --- Mar, 2010\ \ Custom Exteriors of Wisconsin, Inc.

Database~Development and Management~Specialist

{\bfseries
\ \ Development Skills:\ \ AJAX, CSS, Database~Design, HTML, JavaScript, MySQL, Perl, PHP, Technical~Writing}

{\bfseries
\ \ UNIX Admin Skills:\ \ Apache, Firewalls, Virtual~Hosting, VPN}

\liststyleLi
\begin{itemize}
\item Supervised the upgrade and implementation of the company's existing MySQL database
\item Oversaw the development of a comprehensive intranet-based PHP data entry interface for internal company use
\item Wrote and revised technical manuals and employee training programs for the new software infrastructure
\end{itemize}
\ \ Mar, 2009 --- Aug, 2009\ \ Winner, Wixson \& Pernitz

Accounting Data Management Specialist

{\bfseries
\ \ Development Skills:\ \ Perl, Shell}

{\bfseries
\ \ UNIX Admin Skills:\ \ Sendmail, VPN}

\liststyleLi
\begin{itemize}
\item Responsible for the entry and management of thousands of invoices and hand-written work, quickly finding and correcting problems that arose, overseeing billing and mailing operations
\item Managed a complex database of financial information of hundreds of legal clients
\item Supervised the maintenance and upgrade of client and server software and hardware for the entire office
\item Built a replacement internal database in Microsoft Access and a Visual Basic user interface
\end{itemize}
\ \ Jan, 2009 --- Mar, 2009\ \ Custom Exteriors of Wisconsin, Inc.

Outside Technical Consultant

{\bfseries
\ \ Development Skills:\ \ Database~Design, MySQL, Perl, PHP, XML, XSLT}

{\bfseries
\ \ UNIX Admin Skills:\ \ Firewalls, Network~Security, TCP/IP}

\liststyleLi
\begin{itemize}
\item Oversaw the design and launch of a large-scale MySQL database to store financial and work records for thousands of customers and employees
\end{itemize}
\ \ Jul, 2008 --- Jan, 2009\ \ UW-Madison EH\&S

Web Portal Contact Training Specialist

{\bfseries
\ \ Development Skills:\ \ CSS, HTML, JavaScript, Perl, XML}

{\bfseries
\ \ UNIX Admin Skills:\ \ Code~Security, CUPS}

{\bfseries
\ \ Graphic Design Skills:\ \ Inkscape, Photography, The~GIMP}

\liststyleLi
\begin{itemize}
\item Chief designer and developer of a complex website to convey a multitude of safety and medical information
\item Supervised the design of an intuitive and sleek website layout using HTML and CSS
\item Employed advanced graphic and video presentation techniques to a wide range of multimedia for use in a web-based setting
\item Used digital photography and image manipulation techniques in The~GIMP to convey information to a wide audience of hundreds of university workers
\item Employed HTML, CSS and object-oriented JavaScript to create an intuitive user experience
\end{itemize}
\ \ Sep, 2005 --- Present\ \ Youth Against War and Racism

Political Organizer

{\bfseries
\ \ Graphic Design Skills:\ \ Photography, The~GIMP, Inkscape}

\liststyleLi
\begin{itemize}
\item Used advanced graphic design techniques to create dozens of conspicuous and eye-catching materials
\end{itemize}
\ \ Sep, 2005 --- May, 2006\ \ Walgreens, Stillwater, MN

Photo Technician

\ \ Feb, 2001 --- Sep, 2005\ \ Walgreens, Minneapolis, MN

CSR/Photo Technician

\liststyleLi
\begin{itemize}
\item Successfully maintained general retail responsibilities, including accurately counting currency and aiding customers
\item Employed film and print development techniques on four separate machines: Gretag Master Lab Plus; Noritsu QSF-V50 Film Processor and Scanner; Noritsu QSS-35 Plus Print Processor; Fujifilm Minilab-Frontier LP 7000
\end{itemize}
\subsection[Other Skills and Experience]{Other Skills and Experience}
\ \ \textstyleStrongEmphasis{Development:}\ \ \textstyleBulletSymbols{${\bullet}$}\ \ More than 8 years experience programming in Perl~5 using object\nobreakdash-oriented and threaded models.

\liststyleLi
\begin{itemize}
\item Years of experience writing PHP~5, XHTML, CSS~2, JavaScript, AJAX, XML and XSLT.
\item Vast working knowledge of Perl, POSIX and Java regular~expression libraries.
\item Years of experience in UNIX shell~scripting, automated tasks, code~security practices and multithreading.
\item Experience developing Java applications and experience using the Eclipse development platform.
\item Over 2 years experience working in a managed code environment using Subversion and Git.
\item Experience creating object\nobreakdash-oriented code libraries in Perl, PHP and Java. Published on CPAN.
\item Experience building and using databases using SQLite, MySQL and PostgreSQL and working with PHP and Perl APIs.
\item Working knowledge of artificial intelligence (AI) programming concepts and designs, constructing and implementing neural~networks.
\end{itemize}
\ \ \textstyleStrongEmphasis{UNIX Administration:}\ \ \textstyleBulletSymbols{${\bullet}$}\ \ Over 8 years experience administrating Linux servers and virtual hosts.

\liststyleLi
\begin{itemize}
\item Vast and intimate knowledge of UNIX system administration, networking and security.
\item Years of Apache, MySQL and virtual~hosting experience.
\item Extensive experience building, setting up and administrating computer networks and clusters.
\item Experience building desktop computers and upgrading hardware.
\end{itemize}
\ \ \textstyleStrongEmphasis{Graphic Design:}\ \ \textstyleBulletSymbols{${\bullet}$}\ \ Years of 2D and 3D graphic design experience working with Inkscape, The~GIMP, Blender, Dia, Scribus, Adobe~Photoshop and Illustrator.

\liststyleLi
\begin{itemize}
\item Experience developing visual media in OpenOffice, LibreOffice and Microsoft~Office.
\item Experience constructing, editing, encoding and analyzing digital audio with working knowledge of audio filtering types and techniques.
\end{itemize}
\subsection[References]{References}
\begin{table}
\centering
\begin{tabular}{m{2.5358598in}|m{2.5365598in}}

\centering{\sffamily\bfseries Employment} &
\centering\arraybslash{\sffamily\bfseries Employment}\\
{\sffamily Walsh, Andrew} &
{\sffamily Paul, Becky}\\
{\sffamily Custom Exteriors of WI, Inc} &
{\sffamily Winner, Wixson \& Pernitz}\\
{\sffamily 3501 N Northridge Ln\newline
Appleton, WI 54914} &
{\sffamily 22 E. Mifflin St Suite 702\newline
Madison, WI 53701}\\
{\sffamily Tel: +1-920-810-4306} &
{\sffamily Tel: +1-608-257-0257}\\
\multicolumn{1}{m{2.5358598in}}{~
} &
~
\\
\centering{\sffamily\bfseries Employment} &
\centering\arraybslash{\sffamily\bfseries Employment}\\
{\sffamily Discher, Michelle} &
{\sffamily Morrison, Jim}\\
{\sffamily UW-Madison EH\&S} &
{\sffamily UW-Madison EH\&S}\\
{\sffamily 30 East Campus Mall\newline
Madison, WI 53715} &
{\sffamily 30 East Campus Mall\newline
Madison, WI 53715}\\
{\sffamily Tel: +1-608-890-0320} &
{\sffamily Tel: +1-608-263-2177}\\
\multicolumn{1}{m{2.5358598in}}{~
} &
~
\\
\centering{\sffamily\bfseries Employment} &
\centering\arraybslash{\sffamily\bfseries Employment}\\
{\sffamily Madsen, Brandon} &
{\sffamily Larsen, Matthew}\\
{\sffamily Youth Against War and Racism} &
{\sffamily Walgreens \#01811}\\
{\sffamily 345 W Doty St \#2\newline
Madison, WI 53703} &
{\sffamily 3207 E Lake St\newline
Minneapolis, MN 55406}\\
{\sffamily Tel: +1-608-251-6258} &
{\sffamily Tel: +1-612-721-4114}\\
\multicolumn{1}{m{2.5358598in}}{~
} &
~
\\
\centering{\sffamily\bfseries Personal} &
\centering\arraybslash{\sffamily\bfseries Personal}\\
{\sffamily Shillingford, Nick} &
{\sffamily Stanislowski, Cryztal}\\
~
 &
~
\\
{\sffamily 1029 State St \#33\newline
River Falls, WI 54022} &
{\sffamily 3809 Sibley St \#207,\newline
Burnsville, MN 55337}\\
{\sffamily Tel: +1-612-251-0707} &
{\sffamily Tel: +1-952-457-1475}\\\end{tabular}

\end{table}

\bigskip
\end{document}
